\section{Experiments}
\subsection{Environments}
We have devised a custom task for experimentation named
construction. A custom task was selected over a pre-existing ICL
environments due to the fact that these tasks are solvable without the
need for creative problem solving.

The construction task consists of a single domain file that includes
the actions `smash-cover`, `hit-nail`, `turn-bolt`, and
`turn-screw`. These actions require various tools: `hammer`, `wrench`,
and `screwdriver`.

\subsection{Evaluation Framework}
The accompanying problem files can be seperated into categories ---
standard, bulk, no substitution, stress, and chained.

The standard test case consists of a handful of tools and goal wherein
the tool traditionally used to solve the goal is missing. For example,
consider a problem where the agent needs to hammer in a loose nail but
does not have hammer. In these standard problems one of the tools can
be validly substituted as a hammer to solve the goal.

The bulk test case is a modification of standard wherein the goal
consists of multiple parts and thus requires multiple substititions.

Chained problems require more steps to reach the goal.

No substitution problems are impossible, wherein no substitution can
be made to make the task solvable.

Stress problems have many more tools available for substitution. This
test is meant to explore how the LLM scales to more distractor tools.

We have also devised an experiment to test how the LLMs adjust to
different environment semantics. The problem files for this experiment
are based on the stress test case. For each problem, we use an Claude
Sonnet 4.6 to substitute tools, and other objects, with synonyms.

\subsection{Prompt Iteration}
LLMs were used to refine the prompts {...}

\subsection{Experiment Details}
Pyperplan was used, is not state of the art but since we are not evaluating performance that is ok {...}
