\section{Introduction}
As open-world robotics grows to be more prevelant is it crucial to
explore ways that robots can adapt to novelties. Recent work has
focused on end-to-end learning systems where deep-learning models are
responsible for processing sensory inputs and outputting physical
actuations. These systems offer no gaurentees on safety or optimality,
but may be more capable in a variety of dynamic tasks. On the other
hand, traditional symbolic systems may offer safety and optimality
gaurentees at the cost of being significantly less adaptable to
environmental noveleties.

Symbolic approaches require strict representations of robot
affordances, and the objects which they can be applied to. Consider
the task of erasing a white-board. if a task-critical object like an
eraser is missing, a traditional symbolic planner would be unable to
yield a solution. An end-to-end approach may still be able to solve
this task by substituting an eraser with a comparable object like a
tissue. However, given that large models are prone to hallucinations,
it is also possible that an end-to-end approach would fail some
percentage of the time.

An important question moving forward is determining how to combine the
desirable qualities from each approach --- the flexibility of
deep-learning approaches and the determinstic nature of symbolic
planning. In this work, we purpose using an LLM to dynamically type a
symbolic problem at run time to add adaptability to novelties. We
evaluate our approach in a variety of creative-problem tasks against
an pre-existing LLM planning benchmark.
