\section{Related Works}
\subsection{Creative Problem Solving}
Creative problem solving can be described as a failure in an agents
understanding of the world such that it is insufficient to complete a
given task \cite{ijcai2023p777}. Existing literature has explored
various approaches to this problem. In one line of work reinforcement
learning (RL) is used to discover action primitaves after reaching an
unrecoverable state \cite{rapid_learn, lorang_rsj_2024}. Gizzi et al.,
propose a system that enumerates action-object combinations after
reaching a failure case \cite{gizzi_ieee_2019}. Rather than learning
entirely new action primitaves or having to test many different
action-object pairs, our approach seeks to use an LLM to offer object
substitions.

\subsection{LLMs for Planning}
The use of LLMs for symbolic planning has been widely explored, with
mixed results. Silver et al. find that LLMs succeed on some symbolic
planning tasks but fail on others
\cite{silverPDDLPLANNINGPRETRAINED2022}, and subsequent benchmarking
work has confirmed that LLMs do not reliably produce correct plans
\citep{valmeekam_large_nodate,
valmeekam2023planbenchextensiblebenchmarkevaluating}. Despite these
limitations, LLMs have shown promise as components within larger
planning pipelines rather than as end-to-end planners.

One direction leverages LLMs for problem formulation and
decomposition. Liu et al. use LLMs to generate PDDL problem files from
natural language descriptions \citep{liu_llmp_2023}, while Singh et
al. demonstrate that, in a two-agent setting, LLMs can decompose
problems into simpler sub-tasks amenable to parallel execution
\citep{singh_twostep_2024}. Researchers have similarly integrated LLMs
into Hierarchical Task Networks to break high-level goals into more
tractable sub-tasks \citep{pmlr-v288-munoz-avila25a, xu2025online}.

A second direction uses LLM-generated outputs to guide or improve
search and learning. Silver et al. propose treating an LLM-generated
plan — even an incorrect one — as a heuristic to guide greedy
best-first search \citep{silverPDDLPLANNINGPRETRAINED2022}, and Hazra
et al. similarly incorporate heuristics to improve LLM-based planning
\citep{hazra_saycanpay_2024}. Kambhampati et al. take a complementary
approach, employing critics to evaluate and refine plans produced by
LLMs \citep{kambhampati_llms_2024}. Researchers have also explored
using LLMs' code generation capabilities to produce programs that
solve specific tasks \citep{silver2024generalized}.
